### 2017-05-22 2017mergingmerges/section/02-Processes.tex
Fixing typos and wibbles

Finally, the instruction @(drop sIn1 A0 [])@ signals that the current element that was pulled from stream @sIn1@ is no longer required, and goes back to the first the instruction at @A0@.

>>>>

Finally, the instruction @(drop sIn1 A0 [])@ signals that the current element that was pulled from stream @sIn1@ is no longer required, and goes back to the first instruction at @A0@.
